---
title: 2019 Love Live! Song Popularity Poll Results
output:
  html_document:
    includes:
      in_header: "favicon.html"
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
library(magrittr)
library(ggplot2)
library(dplyr)
library(kableExtra)
knitr::opts_chunk$set(echo=FALSE, fig.width=12, fig.align="center")

vote_totals <- readRDS("C:\\Users\\Bearkey\\Documents\\Anime\\lovelive\\data\\assets\\lovelive_pollresults_plotready.rds")
song_color_map <- readRDS("C:\\Users\\Bearkey\\Documents\\Anime\\lovelive\\data\\assets\\lovelive_songcolormap.rds")
seiyuu_color_map <- readRDS("C:\\Users\\Bearkey\\Documents\\Anime\\lovelive\\data\\assets\\lovelive_seiyuucolormap.rds")
song_outline <- readRDS("C:\\Users\\Bearkey\\Documents\\Anime\\lovelive\\data\\assets\\lovelive_songoutline.rds")
metadata <- readRDS("C:\\Users\\Bearkey\\Documents\\Anime\\lovelive\\data\\assets\\lovelive_metadata.rds")
get_ggplot <- function(qnum) {
  type <- filter(vote_totals, question_no==qnum)[1,"q_type"]
  if (type=="song") {
    color_map <- song_color_map
  } else {
    color_map <- seiyuu_color_map
  }
  df <- filter(vote_totals, question_no==qnum)
  base <- ggplot(df, aes(reorder(song, votes), votes))+
    coord_flip()+
    scale_fill_manual(values=color_map)+
    labs(y="Number of votes")+
    theme_bw()+
    theme(legend.position="bottom", axis.title.y=element_blank(), axis.text=element_text(size=12), axis.title.x=element_text(size=12), legend.text=element_text(size=12))+
    scale_y_continuous(expand=expand_scale(mult=c(0, 0.13)))
  if (type=="song") {
    gg <- base+geom_bar(stat="identity", aes(fill=Artist, col=Artist), size=1.2)+scale_color_manual(values=song_outline)
    if (length(unique(df$Artist))==1) gg <- gg+theme(legend.position="none")
  } else {
    gg <- base+geom_bar(stat="identity", aes(fill=song))+theme(legend.position="none")
  }
  return(gg+geom_text(aes(label=paste(votes, prop, sep=", ")), hjust=-0.05))
}
tstyle <- function(df) {
  df %>%
    kable("html") %>% 
    kable_styling(bootstrap_options="striped", full_width=FALSE)
}
```

<br/>

#Introduction

---

##Acknowledgements

This document displays Love Love! song popularity results from [an online poll](https://www.reddit.com/r/SchoolIdolFestival/comments/c9htvz/hello_ive_made_a_poll_that_ranks_the_popularity/), which was created by [u/a-large-bee](https://www.reddit.com/user/a-large-bee) aka [idolfestivals](https://idolfestivals.tumblr.com/) and was open from July 5 to 8, 2019. The OP released the poll results in [this reddit post](https://www.reddit.com/r/SchoolIdolFestival/comments/cb70qb/2019_song_popularity_poll_results/). Many thanks to the OP for creating the opportunity to gauge the opinions of the wider Love Live! community.

##Some general poll statistics

In total, the poll received 734 ballots. However, the poll recorded 719 ballots after removing ballots whose respondents did not answer at least one question (e.g. the ballot was blank). As indicated by the OP in the results document, the poll was disseminated online through [the SchoolIdolFestival subreddit](https://www.reddit.com/r/SchoolIdolFestival/) and [Tumblr](https://idolfestivals.tumblr.com/).

Out of the 28 questions in the poll, 13 questions were related to Love Live! School Idol Project, 13 questions were related to Love Live! Sunshine!!, and 2 questions were related to PERFECT Dream Project.

##Author Notes

The motivation for this document was to visualize the poll results in a cleaner format. I take no credit for the poll and have merely used its results to make plots. I would also appreciate any feedback on the data visualization and presentation. Any feedback on the original poll should be directed to the OP.

In this document, each question is accompanied by a bar plot of its responses and a table containing background information on the responses. The table contains three statistics for the given question:

* Number of ballots: the number of ballots received for the question (equivalent to the number of respondents who answered the question),
* Number of votes: the number of votes received for the question (since a ballot could contain multiple votes for a given question if the question allowed multiple selections),
* Vote limit: the maximum number of votes allowed for the given question per respondent.

Where relevant, the bars in the bar plot are colored according to a color legend. For the purpose of this color coding, all unnamed subgroups are referred to as a "small group" of the associated larger group. For example, the artist of the song "Manatsu wa Dare no Mono?" would count as "Aqours small group" because the combination of Dia and Ruby is not officially named (technically the name is "Inferno Phoenix," but this is beside the point).

<br/>

#Section 1: Love Live! School Idol Project

---

##1. Which are your favorite µ's songs from Love Live! School Idol Project season 1?

```{r}
get_ggplot(1)
tstyle(metadata[[1]])
```

##2. Which are your favorite µ's songs from Love Live! School Idol Project Season 2?

```{r}
get_ggplot(2)
tstyle(metadata[[2]])
```

##3. Which are your favorite µ's songs from Love Live! The School Idol Movie?

```{r}
get_ggplot(3)
tstyle(metadata[[3]])
```

##4. Which are your favorite non-insert µ's songs?

```{r fig.asp=1.5}
get_ggplot(4)
tstyle(metadata[[4]])
```

##5. Which are your favorite BiBi songs?

```{r}
get_ggplot(5)
tstyle(metadata[[5]])
```

##6. Which are your favorite lily white songs?

```{r}
get_ggplot(6)
tstyle(metadata[[6]])
```

##7. Which are your favorite Printemps songs?

```{r}
get_ggplot(7)
tstyle(metadata[[7]])
```

##8. Which are your favorite small group songs?

```{r}
get_ggplot(8)
tstyle(metadata[[8]])
```

##9. Which are your favorite solo songs?

```{r fig.asp=1.2}
get_ggplot(9)
tstyle(metadata[[9]])
```

##10. Which is your favorite A-RISE song?

```{r}
get_ggplot(10)
tstyle(metadata[[10]])
```

##11. Out of every song from this section, which is your favorite?

```{r fig.asp=3}
get_ggplot(11)
tstyle(metadata[[11]])
```

##12. Which is your favorite MV?

```{r fig.asp=1.2}
get_ggplot(12)
tstyle(metadata[[12]])
```

##13. Which µ's member is your favorite singer?

```{r}
get_ggplot(13)
tstyle(metadata[[13]])
```

<br/>

#Section 2: Love Live! Sunshine!!

---

##1. Which are your favorite Aqours songs from Love Live! Sunshine!! season 1?

```{r}
get_ggplot(14)
tstyle(metadata[[14]])
```

##2. Which are your favorite Aqours songs from Love Live! Sunshine!! season 2?

```{r}
get_ggplot(15)
tstyle(metadata[[15]])
```

##3. Which are your favorite Aqours songs from Love Live! The School Idol Movie: Over The Rainbow?

```{r}
get_ggplot(16)
tstyle(metadata[[16]])
```

##4. Which are your favorite non-insert Aqours songs?

```{r fig.asp=1.2}
get_ggplot(17)
tstyle(metadata[[17]])
```

##5. Which are your favorite Guilty Kiss songs?

```{r}
get_ggplot(18)
tstyle(metadata[[18]])
```

##6. Which are your favorite AZALEA songs?

```{r}
get_ggplot(19)
tstyle(metadata[[19]])
```

##7. Which are your favorite CYaRon! songs?

```{r}
get_ggplot(20)
tstyle(metadata[[20]])
```

##8. Which are your favorite duets/trios?

```{r}
get_ggplot(21)
tstyle(metadata[[21]])
```

##9. Which are your favorite solo songs?

```{r}
get_ggplot(22)
tstyle(metadata[[22]])
```

##10. Which is your favorite Saint Snow song?

```{r}
get_ggplot(23)
tstyle(metadata[[23]])
```

##11. Out of every song from this section, which is your favorite?

```{r fig.asp=3}
get_ggplot(24)
tstyle(metadata[[24]])
```

##12. Which is your favorite MV?

```{r fig.asp=1.2}
get_ggplot(25)
tstyle(metadata[[25]])
```

##13. Which Aqours member is your favorite singer?

```{r}
get_ggplot(26)
tstyle(metadata[[26]])
```

<br/>

#Section 3: PERFECT Dream Project

---

##1. Which is your favorite PERFECT Dream Project song?

```{r}
get_ggplot(27)
tstyle(metadata[[27]])
```

##2. Which PERFECT Dream Project member is your favorite singer?

```{r}
get_ggplot(28)
tstyle(metadata[[28]])
```