---
title: "2019 Love Live! Song Popularity Poll Results"
author: "by [randhash](https://www.reddit.com/user/randhash/){target='_blank'}"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    css: styles.css
    includes:
      in_header: head.html
    toc: true
    toc_depth: 2
    toc_float: true
---

```{r setup, include=FALSE}
library(magrittr)
library(ggplot2)
library(dplyr)
library(stringr)
library(kableExtra)
library(knitr)
opts_chunk$set(echo=FALSE, fig.width=12, fig.align="center")

vote_totals <- readRDS("C:\\Users\\Bearkey\\Documents\\Anime\\lovelive\\data\\assets\\lovelive_pollresults_plotready.rds")
song_color_map <- readRDS("C:\\Users\\Bearkey\\Documents\\Anime\\lovelive\\data\\assets\\lovelive_songcolormap.rds")
seiyuu_color_map <- readRDS("C:\\Users\\Bearkey\\Documents\\Anime\\lovelive\\data\\assets\\lovelive_seiyuucolormap.rds")
song_outline <- readRDS("C:\\Users\\Bearkey\\Documents\\Anime\\lovelive\\data\\assets\\lovelive_songoutline.rds")
metadata <- readRDS("C:\\Users\\Bearkey\\Documents\\Anime\\lovelive\\data\\assets\\lovelive_metadata.rds")
hd <- readRDS("C:\\Users\\Bearkey\\Documents\\Anime\\lovelive\\data\\assets\\lovelive_headers.rds")
hdq <- hd[hd[,1]==2,]
txt1 <- 16
txt2 <- 12
get_ggplot <- function(qnum) {
  type <- filter(vote_totals, question_no==qnum)[1,"q_type"]
  if (type=="song") {
    color_map <- song_color_map
  } else {
    color_map <- seiyuu_color_map
  }
  df <- filter(vote_totals, question_no==qnum)
  base <- ggplot(df, aes(reorder(song, votes), votes))+
    coord_flip()+
    scale_fill_manual(values=color_map)+
    labs(y="Number of votes")+
    theme_bw()+
    theme(legend.position="bottom",
          axis.title.y=element_blank(),
          axis.text=element_text(size=txt1),
          axis.title.x=element_text(size=txt1),
          legend.title=element_text(size=txt2),
          legend.text=element_text(size=txt2))+
    scale_y_continuous(expand=expand_scale(mult=c(0, 0.142)))
  if (type=="song") {
    gg <- base+geom_bar(stat="identity", aes(fill=Artist, col=Artist), size=1.2)+scale_color_manual(values=song_outline)+guides(fill=guide_legend(ncol=4))
    if (length(unique(df$Artist))==1) gg <- gg+theme(legend.position="none")
  } else {
    gg <- base+geom_bar(stat="identity", aes(fill=song))+theme(legend.position="none")
  }
  return(gg+geom_text(aes(label=paste(votes, paste0(round(prop, 1), "%"), sep=", ")), size=txt2*0.352778, hjust=-0.05))
}
tstyle <- function(df) {
  df %>%
    kable("html", col.name=NULL) %>% 
    kable_styling(bootstrap_options="striped", full_width=FALSE)
}
get_disp <- function(i) {
  print(get_ggplot(i))
  print(tstyle(metadata[[i]]))
}
usym <- function(string) {
  escaped <- stringi::stri_escape_unicode(string)
  if (grepl("\\\\u[[:alnum:]]{4}", escaped)) {
    codes <- str_match_all(escaped, "\\\\u([[:alnum:]]{4})")[[1]][,2]
    string <- escaped
    for (i in 1:length(codes)) {
      string <- gsub(paste0("\\\\u", codes[i]), paste0("&#x", codes[i], ";"), string)
    }
  }
  return(gsub("~", "&#126;", string))
}
legart <- function(vec) {
  if (length(unique(na.omit(vec)))>1) {
    return(1)
  } else {
    return(0)
  }
}
sizecalc <- function(c, l, limit=3.2) {
  s <- (0.04*c)+(0.12*l)+0.1
  s[s>=limit] <- limit
  return(s)
}
leg <- vote_totals %>%
  group_by(question_no) %>%
  summarise(legend=legart(Artist)) %>%
  as.data.frame()
plotrows <- vote_totals %>%
  group_by(question_no) %>%
  summarise(count=n()) %>%
  left_join(leg, by="question_no") %>%
  mutate(size=sizecalc(count, legend)) %>%
  as.data.frame()
asp <- plotrows[,"size"]
```

<br/>

#Introduction

---

##Acknowledgements

This document displays Love Love! song popularity results from [an online poll](https://www.reddit.com/r/SchoolIdolFestival/comments/c9htvz/hello_ive_made_a_poll_that_ranks_the_popularity/){target="_blank"}, which was created by [a-large-bee](https://www.reddit.com/user/a-large-bee){target="_blank"} aka [idolfestivals](https://idolfestivals.tumblr.com/){target="_blank"} and was open from July 5 to 8, 2019. The OP released the poll results in [this reddit post](https://www.reddit.com/r/SchoolIdolFestival/comments/cb70qb/2019_song_popularity_poll_results/){target="_blank"}. Many thanks to the OP for creating the opportunity to gauge the opinions of the wider Love Live! community.

##Some general poll statistics

In total, the poll received 734 ballots. However, the poll recorded 719 ballots after removing ballots whose respondents did not answer at least one question (e.g. the ballot was blank). As indicated by the OP in the results document, the poll was disseminated online through [the SchoolIdolFestival subreddit](https://www.reddit.com/r/SchoolIdolFestival/){target="_blank"} and [Tumblr](https://idolfestivals.tumblr.com/){target="_blank"}.

Out of the 28 questions in the poll, 13 questions were related to Love Live! School Idol Project, 13 questions were related to Love Live! Sunshine!!, and 2 questions were related to PERFECT Dream Project.

##Author Notes

The motivation for this document was to visualize the poll results in a cleaner format. I take no credit for the poll and have merely used its results to make plots. I would also appreciate any feedback on the data visualization and presentation. Any feedback on the original poll should be directed to the OP.

In this document, each question is accompanied by a bar plot of its responses and a table containing background information on the responses. The table contains three statistics for the given question:

* Number of ballots: the number of ballots received for the question (equivalent to the number of respondents who answered the question),
* Number of votes: the number of votes received for the question (since a ballot could contain multiple votes for a given question if the question allowed multiple selections),
* Vote limit: the maximum number of votes allowed for the given question per respondent.

Where relevant, the bars in the bar plot are colored according to a color legend. For the purpose of this color coding, all unnamed subgroups are referred to as a "small group" of the associated larger group. For example, the artist of the song "Manatsu wa Dare no Mono?" would count as "Aqours small group" because the combination of Dia and Ruby is not officially named (technically the name is "Inferno Phoenix," but this is beside the point).

```{r include=FALSE}
src <- lapply(1:nrow(hd), function(i) knit_expand(file="display.Rmd"))
```

`r knit(text=unlist(src))`

<br/>

#Some random observations

---

##Responses with the most votes {.tabset}

###By raw vote total

```{r}
tstyle2 <- function(df) {
  df %>%
    kable("html") %>% 
    kable_styling(bootstrap_options="striped", full_width=FALSE)
}
vote_totals <- rename(vote_totals, Response=song, Votes=votes, Question=question, Percentage=prop)
vote_totals %>%
  arrange(desc(Votes)) %>%
  head(10) %>%
  select(Response, Question, Votes) %>%
  tstyle2()
```

###By adjusted vote total (Votes/Average number of votes per respondent)

```{r}
avg_resp <- function(df) df[2,2]/719
vote_totals %>%
  left_join(data.frame(question_no=1:length(metadata), avg_votes=sapply(metadata, avg_resp)), by="question_no") %>%
  mutate(`Adjusted votes`=round(Votes/avg_votes, 2)) %>%
  arrange(desc(`Adjusted votes`)) %>%
  head(10) %>%
  select(Response, Question, `Adjusted votes`) %>%
  tstyle2()
```

* The average number of votes per respondent for a given question takes into account a respondent even if the respondent did not answer the question. The respondent is merely counted as providing 0 votes for the question. This interpretation has the caveat that this respondent answered at least one other question (or else the respondent would have already been removed as a blank ballot).

##Responses with the highest percentages

```{r}
vote_totals %>%
  arrange(desc(Percentage)) %>%
  head(10) %>%
  select(Response, Question, Percentage) %>%
  mutate(Percentage=round(Percentage, 2)) %>%
  tstyle2()
```

##Responses with the largest winning margins by percentage

```{r}
mrg <- function(vec) vec[1]-vec[2]
margindf <- vote_totals %>%
  arrange(question_no, desc(Percentage)) %>%
  group_by(question_no) %>%
  summarise(`Margin (%)`=mrg(Percentage)) %>%
  as.data.frame()
vote_totals %>%
  group_by(question_no) %>%
  filter(Percentage==max(Percentage)) %>%
  left_join(margindf, by="question_no") %>%
  arrange(desc(`Margin (%)`)) %>%
  head(10) %>%
  mutate(`Margin (%)`=paste0("+", round(`Margin (%)`, 1))) %>%
  ungroup() %>%
  select(Response, Question, `Margin (%)`) %>%
  as.data.frame() %>%
  tstyle2()
```

##Questions with the most/fewest number of ballots {.tabset}

###Most

```{r}
questiondf <- vote_totals %>%
  select(question_no, Question) %>%
  unique()
metadf <- plyr::rbind.fill(metadata) %>%
  mutate(question_no=rep(1:length(metadata), each=3))
metadf %>%
  filter(stat=="Number of ballots: ") %>%
  arrange(desc(value)) %>%
  head(7) %>%
  left_join(questiondf, by="question_no") %>%
  select(Question, Ballots=value) %>%
  tstyle2()
```

###Fewest

```{r}
metadf %>%
  filter(stat=="Number of ballots: ") %>%
  arrange(value) %>%
  head(7) %>%
  left_join(questiondf, by="question_no") %>%
  select(Question, Ballots=value) %>%
  tstyle2()
```

##Average number of votes per respondent by question

```{r}
metadf %>%
  filter(stat=="Number of votes: ") %>%
  mutate(av=value/719) %>%
  mutate(`Vote limit`=filter(metadf, stat=="Vote limit: ")[,2]) %>%
  mutate(`Response rate (%)`=round((av/`Vote limit`)*100, 2)) %>%
  mutate(`Avg votes`=round(av, 2)) %>%
  left_join(questiondf, by="question_no") %>%
  select(Question, `Avg votes`, `Vote limit`, `Response rate (%)`) %>%
  as.data.frame() %>%
  tstyle2()
```

* The average number of votes per respondent for a given question takes into account a respondent even if the respondent did not answer the question. The respondent is merely counted as providing 0 votes for the question. This interpretation has the caveat that this respondent answered at least one other question (or else the respondent would have already been removed as a blank ballot).

<br/>

#Song Index

---

```{r results="asis"}
linkdf <- vote_totals %>%
  filter(q_type=="song") %>%
  select(Response, question_no) %>%
  arrange(Response, question_no)
uniq <- unique(linkdf[,"Response"])
brk <- ceiling(length(uniq)/2)+1
labcon <- function(index) {
  lab <- index %% 13
  return(ifelse(lab==0, 13, lab))
}
cat("\n<div class='row'>\n")
for (i in 1:length(uniq)) {
  song <- uniq[i]
  qno <- filter(linkdf, Response==song)[,"question_no"]
  if (i==1) {
    cat("\n<div class='column'>\n")
  } else if (i==brk) {
    cat("\n</div>\n")
    cat("\n<div class='column'>\n")
  }
  cat(paste0("\n", usym(song), ": ", paste(paste0("[", paste0(ceiling(qno/13), ".", labcon(qno)), "](#q", qno, ")"), collapse=", "), "\n"))
}
cat("\n</div>\n")
cat("\n</div>\n")
```

<br/>

#References

---

* a-large-bee. "2019 Song Popularity Poll Results." r/SchoolIdolFestival. Last modified July 9, 2019. Accessed July 9, 2019. [https://www.reddit.com/r/SchoolIdolFestival/comments/cb70qb/2019_song_popularity_poll_results](https://www.reddit.com/r/SchoolIdolFestival/comments/cb70qb/2019_song_popularity_poll_results/){target="_blank"}.
* Love Live! Wikia. Accessed July 12, 2019. [https://love-live.fandom.com](https://love-live.fandom.com/){target="_blank"}.