<br/>

#Section 1: Love Live! School Idol Project

---

##1. Which are your favorite µ's songs from Love Live! School Idol Project season 1?

```{r eval=FALSE}
get_ggplot(1)
tstyle(metadata[[1]])
```

##2. Which are your favorite µ's songs from Love Live! School Idol Project Season 2?

```{r eval=FALSE}
get_ggplot(2)
tstyle(metadata[[2]])
```

##3. Which are your favorite µ's songs from Love Live! The School Idol Movie?

```{r}
get_ggplot(3)
tstyle(metadata[[3]])
```

##4. Which are your favorite non-insert µ's songs?

```{r fig.asp=1.5}
get_ggplot(4)
tstyle(metadata[[4]])
```

##5. Which are your favorite BiBi songs?

```{r}
get_ggplot(5)
tstyle(metadata[[5]])
```

##6. Which are your favorite lily white songs?

```{r}
get_ggplot(6)
tstyle(metadata[[6]])
```

##7. Which are your favorite Printemps songs?

```{r}
get_ggplot(7)
tstyle(metadata[[7]])
```

##8. Which are your favorite small group songs?

```{r}
get_ggplot(8)
tstyle(metadata[[8]])
```

##9. Which are your favorite solo songs?

```{r fig.asp=1.2}
get_ggplot(9)
tstyle(metadata[[9]])
```

##10. Which is your favorite A-RISE song?

```{r}
get_ggplot(10)
tstyle(metadata[[10]])
```

##11. Out of every song from this section, which is your favorite?

```{r fig.asp=3}
get_ggplot(11)
tstyle(metadata[[11]])
```

##12. Which is your favorite MV?

```{r fig.asp=1.2}
get_ggplot(12)
tstyle(metadata[[12]])
```

##13. Which µ's member is your favorite singer?

```{r}
get_ggplot(13)
tstyle(metadata[[13]])
```

<br/>

#Section 2: Love Live! Sunshine!!

---

##1. Which are your favorite Aqours songs from Love Live! Sunshine!! season 1?

```{r}
get_ggplot(14)
tstyle(metadata[[14]])
```

##2. Which are your favorite Aqours songs from Love Live! Sunshine!! season 2?

```{r}
get_ggplot(15)
tstyle(metadata[[15]])
```

##3. Which are your favorite Aqours songs from Love Live! The School Idol Movie: Over The Rainbow?

```{r}
get_ggplot(16)
tstyle(metadata[[16]])
```

##4. Which are your favorite non-insert Aqours songs?

```{r fig.asp=1.2}
get_ggplot(17)
tstyle(metadata[[17]])
```

##5. Which are your favorite Guilty Kiss songs?

```{r}
get_ggplot(18)
tstyle(metadata[[18]])
```

##6. Which are your favorite AZALEA songs?

```{r}
get_ggplot(19)
tstyle(metadata[[19]])
```

##7. Which are your favorite CYaRon! songs?

```{r}
get_ggplot(20)
tstyle(metadata[[20]])
```

##8. Which are your favorite duets/trios?

```{r}
get_ggplot(21)
tstyle(metadata[[21]])
```

##9. Which are your favorite solo songs?

```{r}
get_ggplot(22)
tstyle(metadata[[22]])
```

##10. Which is your favorite Saint Snow song?

```{r}
get_ggplot(23)
tstyle(metadata[[23]])
```

##11. Out of every song from this section, which is your favorite?

```{r fig.asp=3}
get_ggplot(24)
tstyle(metadata[[24]])
```

##12. Which is your favorite MV?

```{r fig.asp=1.2}
get_ggplot(25)
tstyle(metadata[[25]])
```

##13. Which Aqours member is your favorite singer?

```{r}
get_ggplot(26)
tstyle(metadata[[26]])
```

<br/>

#Section 3: PERFECT Dream Project

---

##1. Which is your favorite PERFECT Dream Project song?

```{r}
get_ggplot(27)
tstyle(metadata[[27]])
```

##2. Which PERFECT Dream Project member is your favorite singer?

```{r}
get_ggplot(28)
tstyle(metadata[[28]])
```

<br/>
